# Appendix A : Data Catalogue {-}

## Coorong data categories {-}

All data available for model setup and validation has been compiled, from HCHB research, prior research and routine monitoring (see [Chapter 3](Model-Data Ecosystem)). Data is categorised in the general areas of :

+ *Bathymetry*
+ *Meteorology*
+ *Hydrology*
+ *Water Quality*
+ *Sediment*
+ *Biota*

These are defined into sub-categories, as outlined in Table \@ref(tab:A-dataclasses).

<br>

```{r A-dataclasses, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
theSheet <- read_excel('tables/CDM_Classes.xlsx', sheet = 2)
theSheet <- theSheet[theSheet$Table == "Data",]
theSheetGroups <- unique(theSheet$Group)

kbl(theSheet[,3:4], caption = "CDM Data Classification", align = "l",) %>%

row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```

<br>

## Coorong data catalogue {-}

A summary of the available data categorised by these data types and by agency/supplier is shown below (Table \@ref(tab:A-datacatalogue)). Data is accesible via the `data` folder of the CDM [GitHub repository](https://github.com/AquaticEcoDynamics/CDM/tree/master/data). Please refer to the master data catalogue spreadsheet therein for data provenance information.

<br>
```{r A-datacatalogue, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
theSheet <- read_excel('tables/data_catalogue.xlsx', sheet = 2)
theSheet <- theSheet[theSheet$Table == "Data",]
theSheetGroups <- unique(theSheet$Group)

kbl(theSheet[,4:10], caption = "CDM simulated variable summary", align = "l",) %>%
  pack_rows(theSheetGroups[1],
            min(which(theSheet$Group == theSheetGroups[1])),
            max(which(theSheet$Group == theSheetGroups[1])),
            background = '#ebebeb') %>%
  pack_rows(theSheetGroups[2],
            min(which(theSheet$Group == theSheetGroups[2])),
            max(which(theSheet$Group == theSheetGroups[2])),
            background = '#ebebeb') %>%
  pack_rows(theSheetGroups[3],
					  min(which(theSheet$Group == theSheetGroups[3])),
					  max(which(theSheet$Group == theSheetGroups[3])),
					  background = '#ebebeb') %>%
  pack_rows(theSheetGroups[4],
          	min(which(theSheet$Group == theSheetGroups[4])),
          	max(which(theSheet$Group == theSheetGroups[4])),
          	background = '#ebebeb') %>%
  pack_rows(theSheetGroups[5],
            min(which(theSheet$Group == theSheetGroups[5])),
            max(which(theSheet$Group == theSheetGroups[5])),
            background = '#ebebeb') %>%
  pack_rows(theSheetGroups[6],
            min(which(theSheet$Group == theSheetGroups[6])),
            max(which(theSheet$Group == theSheetGroups[6])),
            background = '#ebebeb') %>%

row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = F,font_size = 10) %>%
  column_spec(2, width_min = "7em") %>%
  column_spec(3, width_max = "19em") %>%
  column_spec(4, width_min = "10em") %>%
  column_spec(5, width_min = "5em") %>%
    scroll_box(width = "700px", height = "4600px",
             fixed_thead = FALSE)
```

<br>


